We use the equal-weight ensemble's 48-hour (rather than 24-hour) test forecast to drive the allocation, because each generator is staged once and cannot be relocated during the event window: optimising over the full 48 hours guards against a peak that lands on the second day, which a 24-hour-only objective would miss. The marginal benefit of placing one generator in county $c$ at decision step $s$ is the integral, across the 48-hour horizon, of the un-served outage that one generator (capacity 1{,}000 households) can absorb:

\[
M_s(c) = \sum_{h=1}^{48} \min\!\bigl( \max(\hat y_{c,t+h} - {\rm consumed}_{s-1}(c,h),\ 0),\ 1000,\ {\rm tracked\_max}(c) \bigr).
\]
The inner $\max(\cdot,0)$ clamps the residual outage so that an over-provisioned hour cannot create negative marginal benefit. The per-hour cap at 1{,}000 is what gives the algorithm its \emph{diminishing returns}: once a generator is placed in county $c$, subsequent generators contribute strictly less because the previously consumed capacity is subtracted. With $k$ identical actions and per-county concave utility, this greedy resource allocation is exact-optimal --- a stronger guarantee than the generic $1{-}1/e$ bound for monotone submodular maximisation [12].

A secondary cap at $\text{tracked\_max}(c)$ is included as a defensive guard for two future scenarios: (i) deployment to jurisdictions smaller than 1{,}000 households, and (ii) prediction pathologies where $\hat y_c$ exceeds the county's actual household count. Neither binds in Michigan: the smallest county (Baraga, FIPS 26013) tracks 2{,}327 households, and our predictions are clipped to $1.5\times$ the historical max in any case. We retain the cap for code generality.

We greedily pick $c^\star_s = \arg\max_c M_s(c)$, deduct the served capacity from $\text{remaining}$, and repeat for $s{=}1,\dots,5$. Multiple generators \emph{may} go to the same county if its remaining served-household-hours after deduction still exceed every other county's marginal --- a feature, not a bug, since stacking generators in a high-impact county is allowed by the project description and is the optimal action when the predicted outage is many times larger than 1{,}000.

Our recommendation is:

\begin{quote}
\centering
\verb|[26163, 26125, 26099, 26161, 26163]|
\end{quote}

\paragraph{Rationale (per-step marginal benefit).}\leavevmode\\
\vspace{-1em}
\begin{table}[H]
\centering
\begin{tabular}{rlrrr}
\toprule
step & county & served-hh-hours & tracked\_max & remaining peak \\
\midrule
  1 & 26163.0 & 38870 & 922,425 & 1537 \\
  2 & 26125.0 & 23896 & 618,124 & 853 \\
  3 & 26099.0 & 14654 & 413,676 & 514 \\
  4 & 26161.0 & 5916 & 174,449 & 240 \\
  5 & 26163.0 & 2310 & 922,425 & 1537 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Limitations.}
(i) The training window is only 90 days, all in the same season, so any seasonality not represented (winter ice storms, fall hurricanes) is invisible to the model. (ii) No future-weather information is available at test time, which fundamentally limits 48-hour predictability of fast-moving convective events. (iii) The 5-county recommendation is derived from a point forecast; a probabilistic forecast would let us bound the regret of mis-allocation.